Plots

### 2022-08-10 sandbox/June 25 Presentation Demo.Rmd
Changes to figures including combined effect of FFPE percent and cosine similarity. Cleanup of previous markdowns and files

---
title: "Friday Presentation Demonstration"
author: "Audrey Mitchell, Marco Ruiz, Soua Yang"
date: "6/23/2021"
output: pdf_document
---

@@

#Show Bayes function, explain inputs and outputs

@@

#set column and row names to names of signatures
colnames(test_nmf$signatures) <- c("Signature 18", "Signature 21")
rownames(test_nmf$contribution) <- c("Signature 18", "Signature 21")
```

@@

```{r}
#G[T>C]A mutation is the most common in Signature 21
#269 times more likely in signature 21 than 18
#Sample 6 is ~100% Signature 21
extract_all_prob("G[T>C]A", 6, test_nmf)
#Sample 5 is ~90% Signature 21
extract_all_prob("G[T>C]A", 5, test_nmf)
#Sample 4 is ~70% Signature 21
extract_all_prob("G[T>C]A", 4, test_nmf)
#Sample 4 is ~50% Signature 21
extract_all_prob("G[T>C]A", 4, test_nmf)
#Sample 3 is ~30% Signature 21
extract_all_prob("G[T>C]A", 3, test_nmf)
#Sample 2 is ~10% Signature 21
extract_all_prob("G[T>C]A", 2, test_nmf)
#Sample 1 is ~0% Signature 21
extract_all_prob("G[T>C]A", 1, test_nmf)
```

@@

```{r}
#G[C>A]A mutation is the most common in Signature 18
#1287 times more likely in signature 18 than 21
#Sample 1 is ~100% Signature 18
extract_all_prob("G[C>A]A", 1, test_nmf)
#Sample 2 is ~90% Signature 18
extract_all_prob("G[C>A]A", 2, test_nmf)
#Sample 3 is ~70% Signature 18
extract_all_prob("G[C>A]A", 3, test_nmf)
#Sample 3 is ~50% Signature 18
extract_all_prob("G[C>A]A", 3, test_nmf)
#Sample 4 is ~30% Signature 18
extract_all_prob("G[C>A]A", 4, test_nmf)
#Sample 5 is ~10% Signature 18
extract_all_prob("G[C>A]A", 5, test_nmf)
#Sample 6 is ~0% Signature 18
extract_all_prob("G[C>A]A", 6, test_nmf)
```

@@

```{r}
#low levels of C[C>T]G mutations in both signatures
#Sample 3 is 90% Signature 18 and 10% Signature 21
extract_all_prob("T[C>T]G", 3, test_nmf)
#Sample 4 is 90% Signature 21 and 10% Signature 18
extract_all_prob("T[C>T]G", 4, test_nmf)
```

@@

@@

```{r}
extract_all_prob("T[C>A]T", "MSS_6", nmf.res)
```

@@

```{r}
load_old_mutational_matrix<- function(filename,mut.order="supplied_results/mut_sig.order.txt") {

@@

```{r}
#create ffpe sample vector of 1000 mutations
ffpe.sample.vector <- create_signature_sample_vector(ffpe.signature.matrix, 1000)
ffpe.sample.vector
signature_cosine_similarity(ffpe.sample.vector, ffpe.signature.matrix)
```

```{r}
#create sample matrix to match ffpe signature
ffpe.sample.matrix <- create_signature_sample_matrix(ffpe.signature.matrix, 10000)
ffpe.sample.matrix
#calculate the cosine similarity between sample matrix and original ffpe matrix
cos_sim_matrix(ffpe.sample.matrix, ffpe.signature.matrix)
#plot original ffpe matrix
plot_96_profile(ffpe.signature.matrix)
#plot our ffpe sample matrix
plot_96_profile(ffpe.sample.matrix)
```

>>>>

---
title: "Friday Presentation Demonstration"
author: "Audrey Mitchell, Marco Ruiz, Soua Yang"
date: "6/23/2021"
output: pdf_document
editor_options: 
  chunk_output_type: inline
---

@@

#Show Bayes function, explain inputs and outputs
function(mutation, sample, nmf_res)

@@

#set column and row names to names of signatures
colnames(test_nmf$signatures) <- c("Signature 18", "Signature 21")
rownames(test_nmf$contribution) <- c("Signature 18", "Signature 21")

plot_96_profile(test_nmf$signatures)
```

@@

```{r}
#G[T>C]A mutation is the most common in Signature 21
#269 times more likely in signature 21 than 18

sample.number <- c(1, 2, 3, 4, 5, 6, 7)
percent.sig21 <- c(0,10,30,50,70,90,100)
sig18.prob <- vector(mode = "double")
sig21.prob <- vector(mode = "double")

for (i in 1:7){
  probs <- extract_all_prob("G[T>C]A", i, test_nmf)
  sig18.prob[[i]]<- probs[1][[1]]
  sig21.prob[[i]]<- probs[2][[1]]
}

x <- data.frame(sample.number, percent.sig21, sig18.prob, sig21.prob)
colnames(x) <- c("Sample", "Percent Signature 21", "Signature 18 Posterior Probability", "Signature 21 Posterior Probability")
view(x)
```

@@

```{r}
sample.number2 <- c(1, 2, 3, 4, 5, 6, 7)
percent.sig21.2 <- c(0,10,30,50,70,90,100)
sig18.prob2 <- vector(mode = "double")
sig21.prob2 <- vector(mode = "double")

for (i in 1:7){
  probs <- extract_all_prob("G[C>A]A", i, test_nmf)
  sig18.prob2[[i]]<- probs[1][[1]]
  sig21.prob2[[i]]<- probs[2][[1]]
}

y <- data.frame(sample.number2, percent.sig21.2, sig18.prob2, sig21.prob2)
colnames(y) <- c("Sample", "Percent Signature 21", "Signature 18 Posterior Probability", "Signature 21 Posterior Probability")
view(y)
```

@@

```{r}
#low levels of C[C>T]G mutations in both signatures
#Sample 3 is 90% Signature 18 and 10% Signature 21
extract_all_prob("T[C>T]G", 2, test_nmf)
#Sample 4 is 90% Signature 21 and 10% Signature 18
extract_all_prob("T[C>T]G", 6, test_nmf)
```

@@

cosmic.sigs <- load_cosmic_matrix()

@@

```{r}
#plot_contribution(nmf.res$contribution, nmf.res$signature, mode = "relative", coord_flip = TRUE)
```

```{r}
#T[C>A]T is one of the peaks of the POLE mutational signature, MSS_6 is a sample with a high proportion of POLE mutations
extract_all_prob("T[C>A]T", "MSS_6", nmf.res)
```

```{r}
#G[C>T]T is a mutation that is present in all 4 mutational signatures, MSI_MLH1HM_15 is a sample with contributions from all 4
extract_all_prob("G[C>T]T", "MSI_MLH1HM_15", nmf.res)
```

@@

```{r}
#function to load ffpe signature
load_old_mutational_matrix<- function(filename,mut.order="supplied_results/mut_sig.order.txt") {

@@

```{r}
#create ffpe sample vector of 1000 mutations
ffpe.sample.vector <- create_signature_sample_vector(ffpe.signature.matrix, 100)
ffpe.sample.vector
signature_cosine_similarity(ffpe.sample.vector, ffpe.signature.matrix)
```

```{r}
#create sample matrix to match ffpe signature
ffpe.sample.matrix <- create_signature_sample_matrix(ffpe.signature.matrix, 100)
ffpe.sample.matrix
#calculate the cosine similarity between sample matrix and original ffpe matrix
cos_sim_matrix(ffpe.sample.matrix, ffpe.signature.matrix)
#plot original ffpe matrix
plot_96_profile(ffpe.signature.matrix)
#plot our ffpe sample matrix
plot_96_profile(ffpe.sample.matrix)
```

```{r}
cosmic.sig6 <- as.matrix(cosmic.sigs[, 6])
sample.sig6 <- create_signature_sample_vector(cosmic.sig6, 200)

ffpe.20mutations <- create_signature_sample_vector(ffpe.signature.matrix, 20)

classification.df <- get_classification_df(list(sample.sig6, sample.ffpe), c("MMR","FFPE"), list(cosmic.sig6, ffpe.sig))

#view(classification.df)
mean(classification.df$misclassification)
```

### 2022-08-10 sandbox/Varying Signature Function Testing.Rmd
Changes to figures including combined effect of FFPE percent and cosine similarity. Cleanup of previous markdowns and files

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MutationalPatterns)
library(NMF)
library(tidyverse)
library(ROCR)
source("bayes_function.R")
source("get_classification_df.R")
```

```{r}
#Load FFPE signature
##Function to load FFPE signature
load_old_mutational_matrix<- function(filename,mut.order="supplied_results/mut_sig.order.txt") {

  mutational.signature = read_tsv(filename)
  mut_mat = read_tsv(mut.order)

  mut.join = mutational.signature %>%
    inner_join(mut_mat)

  order.tri = unique(mut.join$ext.context)

  mut.join = mut.join %>%
    mutate(ext.context = factor (ext.context, levels = order.tri)) %>%
    select(ext.context,prob)

  mut.matrix=as.matrix(sapply(mut.join[,2:ncol(mut.join)], as.numeric))  
  rownames(mut.matrix) = mut.join$ext.context

  return (t(mut.matrix)[,1:96])
}

ffpe.signature <- as.matrix(load_old_mutational_matrix("supplied_results/ffpe.signature.txt"))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(MutationalPatterns)
library(NMF)
library(tidyverse)
library(ROCR)
source("bayes_function.R")
source("get_classification_df.R")
source("simulation.R")
```

```{r}
ffpe.signature <- as.matrix(load_old_mutational_matrix("supplied_results/ffpe.signature.txt"))
```

### 2022-08-10 sandbox/plots.Rmd
Changes to figures including combined effect of FFPE percent and cosine similarity. Cleanup of previous markdowns and files

@@

cos.sim.auc.outliers <- cos.sim.auc.data %>%
  filter(residuals >= quantile(cos.sim.auc.data$residuals, 0.90) | 
         residuals <= quantile(cos.sim.auc.data$residuals, 0.10) | 
         signature %in% c("SBS4"))
```

@@

@@

```{r}
sens.spec.label.points <- sens.spec.data %>%
  filter(signature %in% c("SBS38", "SBS4", "SBS89", "SBS3", "SBS33", "SBS44", "SBS31", "SBS40", "SBS42", "SBS23", "SBS19", "SBS11", "SBS30"))
```

@@

>>>>

```{r}
#Summary Statistics for cos.sim.auc.data
summary(cos.sim.auc.data)
IQR(cos.sim.auc.data$cosine_similarity)
IQR(cos.sim.auc.data$average_auc)
```

@@

cos.sim.auc.outliers <- cos.sim.auc.data %>%
  filter(residuals >= quantile(cos.sim.auc.data$residuals, 0.90) | 
         residuals <= quantile(cos.sim.auc.data$residuals, 0.10) | 
         signature %in% c("SBS4", "SBS6"))
```

@@

auc.scatter

@@

```{r}
sens.spec.label.points <- sens.spec.data %>%
  filter(signature %in% c("SBS38", "SBS4", "SBS6","SBS89", "SBS3", "SBS33", "SBS44", "SBS31", "SBS40", "SBS42", "SBS23", "SBS19", "SBS11", "SBS30"))
```

@@

```{r}
sensitivity.model <- lm(sensitivity ~ cosine_similarity, data = sens.spec.data)
summary(sensitivity.model)
```

```{r}
specificity.model <- lm(specificity ~ cosine_similarity, data = sens.spec.data)
summary(specificity.model)
```

```{r}
auc.model <- lm(average_auc ~ cosine_similarity , data = cos.sim.auc.data)
summary(auc.model)
```

```{r}
summary(sens.spec.data)
IQR(sens.spec.data$sensitivity)
IQR(sens.spec.data$specificity)
```

```{r}
#outer for loop: loop through each COSMIC v3 signature
average.accuracies <- c()
for (x in 1:60){
  signature.accuracy.vec <- c()
  #inner for loop: calculate misclassification rate 10x for each signature
  for (y in 1:10){
    #create a sample vector of 500 mutations for the COSMIC signature corresponding to number x
    sample.vec <- create_signature_sample_vector(signature.matrix.list[[x]],500)
    #Create FFPE sample vector of 500 mutations
    ffpe.sample.vec <- create_signature_sample_vector(ffpe.signature, 500)
    classification.df <- get_classification_df(list(sample.vec, ffpe.sample.vec), c(signature.names[x],"FFPE"), list(signature.matrix.list[[x]], ffpe.signature))
    accuracy = 1 - mean(classification.df$misclassification)
    signature.accuracy.vec[y] <- accuracy
  }
  average.signature.accuracy <- mean(signature.accuracy.vec)
  average.accuracies[x] <- average.signature.accuracy
}
```
